Size-differentiated Export in different Dynamical Regimes in the Ocean

### 2019-03-09 size_differentiated_export.tex

Both model experiments described above were then used to investigate the relationship between ocean dynamics and particle export, using Lagrangian particle-tracking. In this study, particles are considered ``exported" once transported below the depth of the winter mixed layer, which roughly corresponds to the 100 m depth horizon at Station Papa. Choosing the winter mixed layer as the export depth is most appropriate compared to other commonly chosen depth horizons (e.g., compensation depth, euphotic depth, etc.), as it reduces the chances of particles being re-entrained into the mixed layer the following winter \citep{Palevsky_2018}. We first consider the case of conservatives particles that do not remineralize in order to isolate the effects of ocean dynamics on export.

The domain-integrated flux of simulated particles crossing the 100 m export horizon, normalized by the total number of particles in each class (N = 1,971,717), is shown in Figure \ref{fig: particle_export} for both \textit{Papa\_summer} and \textit{Papa\_winter}. As expected, the faster-sinking particles are exported earlier than slower-sinking particles. For \textit{Papa\_summer} specifically, only the two fastest sinking-velocity classes (5 and 1 m/day) are exported within the first 28 days after seeding, while the other sinking-velocity classes do not significantly export particles over this time period ($<$ 5\%). In fact, time series of particle export flux closely follow the curves derived from considering only gravitational sinking (Figure \ref{fig: particle_export}a). The particle flux is therefore exclusively downward, as the sinking rate of the particles in these sinking-velocity classes are larger than the advective sinking velocity ($w_s > w_{flow}$; see Figure \ref{fig: dynamics}).

@@

Time series of particle fluxes in \textit{Papa\_winter} present major differences (Figure \ref{fig: particle_export}b). In every sinking-velocity class, particles reach the export horizon faster than expected from gravitational sinking. This hastened arrival of particles is accentuated as the sinking-velocity decreases, ranging from about 1 day early for particles sinking at 5 m/day, to about 10 days early for particles sinking at a rate of 1 m/day. Sinking-velocity classes that are not expected to reach the export depth within the first 28 days now exhibit a significant net downward export within the first 15 days of the simulation. For example, over 20\% of particles sinking at 0.5 m/day is cumulatively exported within the first 28 days in \textit{Papa\_winter}, versus less than 5\% in \textit{Papa\_summer}. However, particle export is now stretched over longer periods of time due to particle resuspension. In fact, the upward flux of particles in \textit{Papa\_winter} tends to mirror the measured downward flux (Figure \ref{fig: particle_export}b), exhibiting similar features such as the sudden increase in particle flux occurring at day 68 due to a wind impulse generating internal waves (see Figure \ref{fig: Papa_winter}a). These similarities suggest that advecting processes leading to an export flux are mostly reversible (e.g., internal waves, cyclo-geostrophy due to meandering jet). However, the net particle fluxes for all sinking-velocity classes remain generally downward, suggesting that some irreversible mechanisms are also occurring at submesoscales. %\fixme{do those irreversible pathways due to sinking out of the reversible pathway, or due to irreversible mechanisms?}

The biomass export fluxes computed from the particle flux shown in Figure \ref{fig: particle_export} using two different Junge slopes demonstrate that, in the presence of submesoscale dynamics, slow-sinking particles significantly contribute to the total export flux over timescales of days (Figure \ref{fig: biomass_export}b). The quasi steady-state reached in the biomass export flux of the three slowest sinking-velocity classes suggests that biomass export is driven by advective processes rather than gravitational sinking ($w_s<w_{flow}$). However, the 5 m/day particle class still exhibits a peak in the biomass export flux coinciding with the peak expected from a simple one-dimensional gravitational sinking model (Figure \ref{fig: particle_export}), suggesting that the export for this sinking-velocity class tend to be gravitationally-driven.

@@

The presence of submesoscale dynamics therefore both hastens particle export, and increases the number of exported slow-sinking particles, by anywhere between a few percent and tens of percents, depending on the sinking-velocity class. This has large implications on the amount of biomass exported, as slower-sinking particles tend to be far more numerous than faster-sinking particles, despite containing less biomass per particle (i.e., $\xi >3$; see Figure \ref{fig: sinking_velocity_spectrum}). While the normalized particle flux is solely a function of the flow field, the exported biomass also depends on the Junge slope (see Equation (\ref{eq: biomassjungeslope})).

The impact of ocean dynamics on the respective contributions of the different sinking velocity classes to the total exported biomass is fairly intuitive: For a specific Junge slope, the presence of submesoscale dynamics enhances the role played by slower-sinking particles in biomass export and decreases the importance of faster-sinking particles (dashed lines in Figure \ref{fig: biomass_export_remin}). This is a logical result given the observed increase in the particle export flux when submesoscales features are present (Figure \ref{fig: particle_export}). The sinking class dominating export, however, is highly dependent on the Junge slope. As the Junge slope increases, the particle spectrum steepens, and the contribution of slower-sinking particles to the total exported biomass increases. For example, after 28 days, the 1 m/day particle class exports 50\%, 100\%, and 125\% of the biomass exported by the 5 m/day class when $\xi =$ 2, 3, and 4, respectively.

Particles, and specifically slow-sinking ones, are however expected to remineralize on timescales shorter than their export timescale. The impacts of remineralization on export are presented and discussed in Sections \ref{sec: results_remin} and \ref{sec: discussion_particle}.

@@

 Including remineralization of particles (see Equation (\ref{eq: remin_scheme})) significantly impacts the relative importance of sinking and advection to export for each particle class. In \textit{Papa\_summer}, particle export associated with a specific sinking-velocity class is delayed when remineralization is implemented, because particles slow down as they are remineralized (see Equation (\ref{eq: sinking_velocity_remin}) and Figure \ref{fig: biomass_export_remin}). In our simulations, particles sinking at 5 m/day reach the export horizon about 3 hours later when remineralization is included. The impact of remineralization intensifies as the sinking velocity weakens: particles sinking at 1 m/day reach the export horizon 9.5 days later when remineralization is implemented.

@@

 In \textit{Papa\_winter}, particles of all sinking-velocity classes tend to be exported over shorter timescales than in \textit{Papa\_summer} due to stronger vertical velocities (Figure \ref{fig: particle_export}. The difference in the biomass export flux between the cases with and without remineralization is therefore relatively small for the first 5 days of the time series, as particles have not had time to significantly remineralize yet but are already behind exported. As particles age, remineralization has an increasing impact and the difference in the biomass export flux increases at a rate controlled by the remineralization rate defined in (\ref{eq: remin_scheme}). An interesting result to be noticed is the fact that, when $\xi = 4$ and remineralization is implemented, the biomass export flux of the 0.025 m/day sinking-velocity class exceeds the biomass export flux from both the 0.5 and 1 m/day sinking-velocity classes. This result only occurs when a negative slope of the biomass spectrum is combined with remineralization.

@@

Studies investigating submesoscale dynamics traditionally focused on regions where the presence of submesoscale fronts and filaments are established, such as western boundary currents with strong gradients \citep{Dasaro_2011, Thomas_2013}, or at the edge of mesoscale features \citep{vanHaren_2006,Waite_2016}. The seasonality in submesoscale dynamics captured in the glider dataset at Station Papa, and reflected in the model experiments, echoes findings of recent observational studies conducted at a similar latitude in the Atlantic Ocean demonstrating the intensification of submesoscale dynamics in the wintertime \citep{Thompson_2016, Buckingham_2016}. Despite being sometimes qualified as an ``eddy desert" with low kinetic energy \citep{Chelton_2011}, wintertime ocean characteristics in the eastern part of the Pacific subpolar gyre suggest the presence of submesoscale features: strong density gradients, localized Rossby numbers of order 1, a balanced Richardson number $Ri_b = \frac{f^2N^2}{M^4}$ smaller than 1, a positively skewed distribution in vorticity, and a negatively skewed distribution of vertical velocities \citep[see Figure \ref{fig: dynamics};][]{Thomas_2008,Rudnick_2001, Buckingham_2016}.

@@

The hypothesis tested in this study is that submesoscale activity enhances export of particulate matter at Station Papa by shortening the export timescale of particulate matter. The wintertime intensification in submesoscale activity has the potential to indeed enhance export (see discussion in Section \ref{sec: discussion_particle}). However, the seasonal cycle in submesoscale activity is out of phase with the one in net community productivity, which peaks in the spring and summertime when the mixed layer is shallower \citep{Plant_2016}. Two mechanisms are therefore present to potentially sustain a year-long POC export: In the winter, less particulate material is present in the mixed layer, but active submesoscale dynamics tend to enhance the POC export by advecting the more numerous slower-sinking particles into the ocean interior. In the summer, the production of POC is at its yearly maximum, but export tends to be dominated by gravitational sinking, which favors faster-sinking particles and thus exclude part of the particle spectrum from contributing to the export flux.

@@

Introducing remineralization processes significantly decreases the biomass export flux. Counter-intuitively, however, remineralization processes further strengthen the impact of submesoscale dynamics on export. The increase in exported biomass when comparing summertime and wintertime is larger when remineralization processes are included, and also increases with larger Junge slopes. This can be explained by the fact that remineralization processes have a greater impact on sinking-velocity classes that rely on gravitational sinking to be exported, as remineralization tends to slow these particles down and thus prolongs their export timescales. In the summer, almost the entirety of the sinking velocity spectrum is therefore affected as all modeled classes rely on gravitational sinking for export. In the winter, however, slower-sinking particles are exported through advective processes. Their export timescale is little affected by remineralization processes as it only depends on local ocean dynamics, leading to a greater net export flux than when remineralization is not considered.

%% this part discusses the respective contributions of the different sinking-velocity classes
The contribution of a particle class to POC export generally increases with the sinking-velocity. That is, faster-sinking particles tend to dominate the export signal and the curve of exported biomass versus sinking-velocity has a positive slope. To have a greater contribution of a slower-sinking velocity class, the following condition must be satisfied:

\begin{equation}
    N_{slow} > N_{fast} \times \left(\frac{w_{s_{fast}}}{w_{s_{slow}}}\right)^{\frac{3 - \xi}{2}}
    \label{eq: condition}
\end{equation}
where $N$ is the number of simulated particles exported, $w_s$ is the sinking velocity and $\xi$ is the Junge slope coefficient (see Equation (\ref{eq: powerlaw_radius})).

In a gravitationally-driven system (i.e., weak submesoscale activity), this can only be achieved by having  $N_{slow} \sim N_{fast}$ and $\xi>3$, as there are no mechanism capable of selectively exporting slower-sinking particles (i.e., $N_{slow} \leq N_{fast}$). Junge slopes greater than 3 are regularly observed in the ocean \citep{Kostadinov_2009, White_2015}. Our results suggest that, in these conditions, the export of biomass is dominated by an intermediate sinking-velocity class that sinks fast enough to be 100\% exported ($N_{slow} = N_{fast}$; see Figure \ref{fig: export_cartoon}a). Because of the negative slope in the biomass spectrum, any particle class sinking at a faster rate will not contribute as much to the biomass export. The intermediate class responsible for the largest part of the export signal will vary with time and space as it depends on the parameter $\xi$, as well as on the export depth. As $\xi$ increases, the sinking-velocity of the dominant class decreases (see Equation (\ref{eq: condition})). A deeper export depth would have the opposite effect and increase sinking-velocity of the dominant class (Figure \ref{fig: export_cartoon}a). Implementing remineralization processes only shifts the curve shown in Figure \ref{fig: export_cartoon}a towards faster-sinking classes: as particle remineralize, a larger portion of the sinking-velocity spectrum will not contribute to POC export, and a faster initial sinking-velocity is required for the export timescale to be shorter than the remineralization timescale.

@@

In a system affected by submesoscale dynamics, localized strong downwelling vertical currents are generated. This effectively shortens the export timescale of slower-sinking particles, entering a regime where export timescales are shorter than remineralization timescales (Figure \ref{fig: export_cartoon}b). In this regime, slower-sinking particles significantly contribute to POC export. In this study, sinking-velocity classes that did not contribute to POC export in a mesoscale regime, are found to contribute up to 30\% of POC export in the most extreme case, where $\xi =4$. Implementing remineralization process has little to no impact on the respective contributions of the different sinking-velocity classes as the impact of remineralization is smaller when export flux is advectively-driven, as opposed to gravitationally-driven.

>>>>

Both model experiments described above were then used to investigate the relationship between ocean dynamics and particle export, using Lagrangian particle-tracking. In this study, particles are considered ``exported" once transported below the depth of the winter mixed layer, which roughly corresponds to the 100 m depth horizon at Station Papa. Choosing the winter mixed layer as the export depth is most appropriate compared to other commonly chosen depth horizons (e.g., compensation depth, euphotic depth, etc.), as it reduces the chances of particles being re-entrained into the mixed layer the following winter \citep{Palevsky_2018}. We first consider the case of conservative particles that do not remineralize in order to isolate the effects of ocean dynamics on export.

The domain-integrated flux of simulated particles crossing the 100 m export horizon, normalized by the total number of particles in each class (N = 1,971,717), is shown in Figure \ref{fig: particle_export} for both \textit{Papa\_summer} and \textit{Papa\_winter}. As expected, the faster-sinking particles are exported earlier than slower-sinking particles. For \textit{Papa\_summer} specifically, only the two fastest sinking-velocity classes (5 and 1 m/day) are exported within the first 28 days after seeding, while the other sinking-velocity classes do not significantly export particles over this time period ($<$ 5\%). In fact, time series of particle export flux closely follow the curves derived from considering gravitational sinking only (Figure \ref{fig: particle_export}a). The particle flux is therefore exclusively downward, as the sinking rate of the particles in these sinking-velocity classes are larger than the advective sinking velocity ($w_s > w_{flow}$; see Figure \ref{fig: dynamics}).

@@

Time series of particle fluxes in \textit{Papa\_winter} present major differences (Figure \ref{fig: particle_export}b). In every sinking-velocity class, particles reach the export horizon faster than expected from gravitational sinking. This hastened arrival of particles is accentuated as the sinking-velocity decreases, ranging from about 1 day early for particles sinking at 5 m/day, to about 10 days early for particles sinking at a rate of 1 m/day. Sinking-velocity classes that are not expected to reach the export depth within the first 28 days now exhibit a significant net downward flux within the first 15 days of the simulation. For example, over 20\% of particles sinking at 0.5 m/day is cumulatively exported within the first 28 days in \textit{Papa\_winter}, versus less than 5\% in \textit{Papa\_summer}. However, particle export is now stretched over longer periods of time due to particle resuspension. In fact, the upward flux of particles in \textit{Papa\_winter} tends to mirror the measured downward flux (Figure \ref{fig: particle_export}b), exhibiting similar features such as the sudden increase in particle flux occurring at day 68 due to a wind impulse generating internal waves (see Figure \ref{fig: Papa_winter}a). These similarities suggest that advecting processes leading to an export flux are mostly reversible (e.g., internal waves, cyclo-geostrophy due to meandering jet). However, the net particle fluxes for all sinking-velocity classes remain generally downward, suggesting that some irreversible mechanisms are also occurring in the presence of submesoscale dynamics. %\fixme{do those irreversible pathways due to sinking out of the reversible pathway, or due to irreversible mechanisms?}

The corresponding biomass export fluxes demonstrate that, in the presence of submesoscale dynamics, slow-sinking particles significantly contribute to the total export flux over timescales of days (Figure \ref{fig: biomass_export}b). The quasi steady-state reached in the biomass export flux of the three slowest sinking-velocity classes suggests that biomass export is driven by advective processes rather than gravitational sinking ($w_s<w_{flow}$). However, the 5 m/day particle class still exhibits a peak in the biomass export flux coinciding with the peak expected from a simple one-dimensional gravitational sinking model, suggesting that the export for this sinking-velocity class remains mostly gravitationally-driven.

@@

The presence of submesoscale dynamics therefore both hastens particle export, and increases the number of exported slow-sinking particles, by anywhere between a few percent and tens of percents, depending on the sinking-velocity class. This has large implications on the amount of biomass exported, as slower-sinking particles tend to be far more numerous than faster-sinking particles, despite containing less biomass per particle (i.e., $\xi >3$; see Figure \ref{fig: sinking_velocity_spectrum}). %While the particle flux is solely a function of the flow field, the exported biomass also depends on the Junge slope (see Equation (\ref{eq: biomassjungeslope})).

The impact of ocean dynamics on the respective contributions of the different sinking velocity classes to the total exported biomass is fairly intuitive: For a specific Junge slope, the presence of submesoscale dynamics enhances the role played by slower-sinking particles in biomass export and decreases the importance of faster-sinking particles (dashed lines in Figure \ref{fig: biomass_export_remin}). This is a logical result given the observed increase in the particle export flux when submesoscale features are present (Figure \ref{fig: particle_export}). The sinking class dominating export, however, is highly dependent on the Junge slope. As the Junge slope increases, the particle spectrum steepens, and the contribution of slower-sinking particles to the total exported biomass increases. For example, after 28 days, the 1 m/day particle class cumulatively exported 50\%, 100\%, and 125\% of the biomass exported by the 5 m/day class when $\xi =$ 2, 3, and 4, respectively. However, slow-sinking particles are generally expected to remineralize on timescales shorter than their export timescale. The impacts of remineralization on export are considered in hthe following section.

@@

 Including remineralization of particles significantly impacts the relative importance of sinking and advection to export for each particle class. In \textit{Papa\_summer}, particle export associated with a specific sinking-velocity class is delayed when remineralization is implemented, because particles decelerate as they are remineralized (see Equation (\ref{eq: sinking_velocity_remin}) and Figure \ref{fig: biomass_export_remin}). In our simulations, particles sinking at 5 m/day reach the export horizon about 3 hours later when remineralization is included. The impact of remineralization intensifies as the sinking velocity weakens: particles sinking at 1 m/day reach the export horizon 9.5 days later when remineralization is implemented.

@@

 In \textit{Papa\_winter}, particles of all sinking-velocity classes tend to be exported over shorter timescales than in \textit{Papa\_summer} due to stronger vertical velocities (Figure \ref{fig: particle_export}). The difference in the biomass export flux between the cases with and without remineralization is therefore relatively small for the first 5 days of the time series, as particles have not had time to significantly remineralize yet but are already being exported. As particles age, remineralization has an increasing impact and the difference in the biomass export flux increases at a rate controlled by the remineralization rate defined in (\ref{eq: remin_scheme}). An interesting result to be noticed is the fact that, when $\xi = 4$ and remineralization is implemented, the biomass export flux of the 0.025 m/day sinking-velocity class exceeds the biomass export flux from both the 0.5 and 1 m/day sinking-velocity classes. This result only occurs when a negative slope of the biomass spectrum is combined with remineralization.

@@

Studies investigating submesoscale dynamics traditionally focused on regions where the presence of submesoscale fronts and filaments are established, such as western boundary currents with strong gradients \citep{Dasaro_2011, Thomas_2013}, or at the edge of mesoscale features \citep{vanHaren_2006,Waite_2016}. The seasonality in submesoscale dynamics captured in the glider dataset at Station Papa, and reflected in the model experiments, echoes findings of recent observational studies conducted at a similar latitude in the Atlantic Ocean demonstrating the intensification of submesoscale dynamics in the wintertime \citep{Thompson_2016, Buckingham_2016}. Despite being sometimes qualified as an ``eddy desert" with low kinetic energy \citep{Chelton_2011}, ocean characteristics in the eastern part of the Pacific subpolar gyre suggest the presence of submesoscale features in the wintertime: strong density gradients, localized Rossby numbers of order 1, a balanced Richardson number $Ri_b = \frac{f^2N^2}{M^4}$ smaller than 1, a positively skewed distribution in vorticity, and a negatively skewed distribution of vertical velocities \citep[see Figure \ref{fig: dynamics};][]{Thomas_2008,Rudnick_2001, Buckingham_2016}.

@@

The hypothesis tested in this study is that submesoscale activity enhances export of particulate matter at Station Papa by shortening the export timescale of particulate matter. The wintertime intensification in submesoscale activity has the potential to indeed enhance export (see discussion in Section \ref{sec: discussion_particle}). However, the seasonal cycle in submesoscale activity is out of phase with the one in net community productivity, which peaks in the spring and summertime when the mixed layer is shallower \citep{Plant_2016}. Two mechanisms are therefore present to potentially sustain a year-long POC export flux: In the winter, less particulate material is present in the mixed layer, but active submesoscale dynamics tend to enhance the POC export flux by advecting the more numerous slower-sinking particles into the ocean interior. In the summer, the production of POC is at its yearly maximum, but export tends to be dominated by gravitational sinking, which favors faster-sinking particles and thus exclude part of the particle spectrum from contributing to the export flux.

@@

Introducing remineralization processes significantly decreases the biomass export flux. Counter-intuitively, however, remineralization processes further strengthen the impact of submesoscale dynamics on export. The difference between summertime and wintertime biomass fluxes is even larger when remineralization processes are included. This can be explained by the fact that remineralization processes have a greater impact on sinking-velocity classes that rely on gravitational sinking to be exported, as remineralization tends to decelrate these particles and thus prolongs their export timescales. In the summer, almost the entirety of the sinking velocity spectrum is therefore affected as export is gravitationally-driven. In the winter, however, slower-sinking particles are exported through advective processes. Their export timescale is little affected by remineralization processes as it only depends on local ocean dynamics.

%% this part discusses the respective contributions of the different sinking-velocity classes
The contribution of a particle class to POC export generally increases with the sinking-velocity. That is, faster-sinking particles tend to dominate the export signal. However, this tendency can be reversed if the following condition is satisfied:

\begin{equation}
    N_{slow} > N_{fast} \times \left(\frac{w_{s_{fast}}}{w_{s_{slow}}}\right)^{\frac{3 - \xi}{2}}
    \label{eq: condition}
\end{equation}
where $N$ is the number of simulated particles exported, $w_s$ is the sinking velocity and $\xi$ is the Junge slope coefficient (see Equation (\ref{eq: powerlaw_radius})). The number of exported slower-sinking particles must therefore be large enough to compensate for the smaller biomass content than faster-sinking particles.

In a gravitationally-driven system (i.e., weak submesoscale activity), this can only be achieved by having  $N_{slow} \sim N_{fast}$ and $\xi>3$, as there are no mechanism capable of selectively exporting slower-sinking particles (i.e., $N_{slow} \leq N_{fast}$). Junge slopes greater than 3 are regularly observed in the ocean \citep{Kostadinov_2009, White_2015}. Our results suggest that, in these conditions, the export of biomass is dominated by an intermediate sinking-velocity class that sinks fast enough to be 100\% exported ($N_{slow} = N_{fast}$; see Figure \ref{fig: export_cartoon}a). Because of the negative slope in the biomass spectrum, the contribution to export of any particle class sinking at a faster rate will be smaller. The intermediate class responsible for the largest part of the export signal will vary with time and space as it depends on the parameter $\xi$, as well as on the export depth. As $\xi$ increases, the sinking-velocity of the dominant class decreases (see Equation (\ref{eq: condition})). A deeper export depth would have the opposite effect and increase sinking-velocity of the dominant class (Figure \ref{fig: export_cartoon}a). %Implementing remineralization processes only shifts the curve shown in Figure \ref{fig: export_cartoon}a towards faster-sinking classes: as particle remineralize, a larger portion of the sinking-velocity spectrum will not contribute to POC export, and a faster initial sinking-velocity is required for the export timescale to be shorter than the remineralization timescale.

@@

In a system affected by submesoscale dynamics, localized strong downwelling vertical currents are generated. This effectively shortens the export timescale of slower-sinking particles, entering a regime where export timescales are shorter than remineralization timescales (Figure \ref{fig: export_cartoon}b). In this regime, slower-sinking particles significantly contribute to POC export. \fixme{In this study, sinking-velocity classes that did not contribute to POC export in a mesoscale regime, are found to contribute up to 30\% of POC export in the most extreme case, where $\xi =4$ Also talk about te fct that it is what we see in Fig 8 with the reveral fo the order.} %Implementing remineralization process has little to no impact on the respective contributions of the different sinking-velocity classes as the impact of remineralization is smaller when export flux is advectively-driven, as opposed to gravitationally-driven.
